SN-\sncode: A Gravitationally-Lensed Type Ia Supernova Candidate at $z=1.95$

### 2020-02-16 Paper/ms.tex
First push from overleaf

\shortauthors{Brammer et al.}
\shorttitle{CHArGE}
% \setwatermarkfontsize{50pt} 
%\citestyle{aa}
\begin{document}

\title{SN-\sncode: A Gravitationally-Lensed Type Ia Supernova Candidate at $z=1.9$}

@@

@@

We report the discovery of a gravitationally-lensed, multiply-imaged transient source with a likely host at $z=1.905$, observed in archival \textit{Hubble Space Telescope} near-infrared imaging observations.

>>>>

\shortauthors{XXX et al.}
\shorttitle{CHArGE}
% \setwatermarkfontsize{50pt} 
%\citestyle{aa}
\begin{document}

\title{SN-\sncode: A Gravitationally-Lensed Type Ia Supernova Candidate at $z=1.95$}

@@

\author[0000-0003-3631-7176]{Sune Toft}
\affiliation{The Cosmic Dawn Center, University of Copenhagen, Vibenshuset, Lyngbyvej 2, DK-2100 Copenhagen, Denmark}

@@

We report the discovery of a gravitationally-lensed, multiply-imaged transient source with a likely host at $z=1.9459$, observed in archival \textit{Hubble Space Telescope} near-infrared imaging observations.
